\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-30 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
add original map before r.diversity
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64945 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
Landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
\end{minipage}

% TODO: some other example or something completely else?
}

@@

Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS};
% http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf

Eva Stopkova for physical model of High Tatras.

>>>>

\bigskip

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_classes}
\end{minipage}
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_shannon}
\end{minipage}

\medskip
Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
}

@@

We acknowledge Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS} and
% http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf
Eva Stopkova for physical model of High Tatras.
